Updated Ephemerides of the young multi-planet system V1298 Tau from TESS

### 2021-10-20 src/ms.tex
some words

\documentclass[twocolumn]{aastex631}

@@

We took a two-step approach to modeling any background contamination. First, we defined a quadratic trend with respect to time for varying the background flux, where each term was drawn from a normal distribution (listed as `trend term' in Table~\ref{tab:table}). Then, we generated a Vandermonde matrix ($A$) of time. This is a way of introducing a polynomial least-squares regression with respect to time. The final background flux was calculated by taking $bkg = A \cdot trend$.

We performed an MCMC sampling fit to each parameter. We ran 4 chains with 500 tuning steps and 3000 draws. We discarded the tuning samples in our final modeling best-fits, presented in Table~\ref{tab:table}. We verified our chains converged via visual inspection and following the diagnostic provided by \cite{Geweke92}.

@@

\subsection{\textit{K2} vs. \tess}

@@

There was a single transit of \planete in the original \textit{K2} data, which occurred roughly in the middle of the campaign. Since no other transits were detected, this provides a lower period limit of 36~days.

@@

A full transit-timing variation (TTV) analysis using \textit{K2}, \textit{Spitzer}, and \tess\ ephemerides is presented in Livingston et al. (in prep).

@@

\begin{deluxetable*}{l r r r r}[!ht]
\tabletypesize{\footnotesize}
\tablecaption{\sname light curve fitting results. \label{tab:table}}
\tablehead{\\
\hline\
\textit{Star} & \textit{Value} & \textit{Prior} &  & \\
\hline
$R_\star [R_\odot]$ & & $\mathcal{G}(1.305, 0.07)$ & & \\
$u_1$ & & & & \\
$u_2$ & & & & \\
$P_{rot}$ [days] & & $\mathcal{G}($ln$ 2.87, 2)$ & & \\
ln($A$ [ppt]) & & & & \\
ln($Q_0$) & & $\mathcal{H}(\sigma=2)$ & & \\
$\Delta Q_0$ & & $\mathcal{G}(0, 2)$ & & \\
$\rho_\textrm{SHO}$ & & $\mathcal{G}(0, 10)$ & & \\
$\sigma_\textrm{SHO}$ & & $\mathcal{G}(\sigma_\textrm{flux}, 10)$ & & \\
f [ppt] & & & & \\
mix & & & & \\
\hline\
\textit{Light Curve} & \textit{Value} & \textit{Prior} &  & \\
\hline
trend term a & & $\mathcal{G}(0, 0.01)$ & & \\
trend term b & & $\mathcal{G}(0, 0.1)$ & & \\
trend term c & & $\mathcal{G}(0, 1)$ & & \\
$\sigma_l$ & & $\mathcal{G}($ln$(0.1\sigma_\textrm{flux}), 10)$  & & \\
$\sigma_j$ & & $\mathcal{G}($ln$(0.1\sigma_\textrm{flux}), 10)$  & & \\
\hline\
\textit{Planets} & \textit{c} & \textit{d} & \textit{b} & \textit{e}\\
\hline
P [days]               &  &  &  &  \\
$T_0$ [BJD - 2457000]  &  &  &  &  \\
Depth [ppt]            &  &  &  &  \\
$R_p/R_\star$          &  &  &  &  \\
$a/R_\star$            &  &  &  &  \\
$b$                    &  &  &  &  \\
$e$ [$^\circ$]         &  &  &  &  \\
\hline\
\textit{Priors} & \textit{c} & \textit{d} & \textit{b} & \textit{e}\\
\hline
log($P$ [days]) & $\mathcal{G}($ln$ 8.25, 1)$ & $\mathcal{G}($ln$ 12.40, 1)$& $\mathcal{G}($ln$ 24.14, 1)$ & $\mathcal{G}($ln$ 36.70, 1)$\\
$T_0$ [BJD - 2457000] & $\mathcal{G}(4648.53,0.1)$ & $\mathcal{G}(4645.4,0.1)$ & $\mathcal{G}(4648.1,0.1)$ & $\mathcal{G}(4648.8,0.1)$ \\
log(depth [ppt]) & $\mathcal{G}($ln$ 1.45, 1)$ & $\mathcal{G}($ln$ 1.90, 1)$ & $\mathcal{G}($ln$ 4.90, 1)$ & $\mathcal{G}($ln$ 3.73, 1)$ \\
$b$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ \\
duration [days] & $\mathcal{G}($ln$ 0.19, 1)$ & $\mathcal{G}($ln$ 0.23, 1)$ & $\mathcal{G}($ln$ 0.27, 1)$ &  $\mathcal{G}($ln$ 0.31, 1)$
}
\startdata
\enddata
\tablecomments{Priors are noted for parameters that were directly sampled. The distributions are as follows -- $\mathcal{G}$: Gaussian; $\mathcal{H}$: Half-normal; $\mathcal{U}$: Uniform. $\sigma_\textrm{flux}$ is the standard deviation of the light curve}
\end{deluxetable*}

@@

\include{table}

>>>>

\documentclass[modern, twocolumn]{aastex631}

@@

We took a two-step approach to modeling any background contamination. First, we defined a quadratic trend with respect to time for varying the background flux, where each term was drawn from a normal distribution (listed as `trend term' in Table~\ref{tab:table}). Then, we generated a Vandermonde matrix ($A$) of time. This is a way of introducing a polynomial least-squares regression with respect to time. The final background flux was calculated by taking $bkg = A \cdot trend$.  
We performed an MCMC sampling fit to each parameter. We ran 4 chains with 500 tuning steps and 3000 draws. We discarded the tuning samples in our final modeling best-fits, presented in Table~\ref{tab:table}. We verified our chains converged via visual inspection and following the diagnostic provided by \cite{Geweke92}.

@@

We find transit timing variations (TTVs) for \planetknown to range from \textcolor{red}{n - n days}. A full TTV analysis using \textit{K2}, \textit{Spitzer}, and \tess\ ephemerides is presented in Livingston et al. (in prep).

\subsection{Differences in Measured Radii}

@@

There was a single transit of \planete in the original \textit{K2} data, which occurred roughly in the middle of the campaign. Since no other transits were detected, this provides a lower period limit of 36~days. Using the original transit timing from \textit{K2} and this new transit timing from \tess, we can place further constraints on the period.

We localized a 1-day window around each transit of \planete and ran a GP fit using \texttt{exoplnaet} for the transit parameters, assuming a constant depth between the \textit{K2} and \tess\ observations. We then compute possible periods 
\begin{equation}
    P = \frac{1}{n} \left(T_{mid,TESS} - T_{mid, K2}\right)
\end{equation}
where $T_{mid}$ are the transit midpoints from \textit{K2} and \tess\ and $n$ is an integer. We then create a light curve using this period, and compute the log-likelihood for the given set of transit parameters. We tested discrete periods ranging from $44- 56$~days. We limit the periods used due to computation time.

Using this method, we constrain the period of \planete to be \textcolor{red}{n}~days. Even at the lower limit, it is unlikely a transit of \planete will occur in the next sector (Sector 44) of \tess\ data for \sname. Independent ground-based monitoring of the system for several days beyond the end of Sector 44 (UT 06 Nov 2021) may be able to observe another transit of the outermost known planet in this system.

@@

We find the transit depths of \allplanets as observed by \tess\ are shallower than previous \textit{K2} observations. We postulate this could be due to ongoing dusty outflows, that make the transit depth appear shallower. However, measuring the transit depths at longer wavelengths could confirm this.

@@

@@

\begin{deluxetable*}{l r r r r}[!ht]
\tabletypesize{\footnotesize}
\tablecaption{\sname light curve fitting results. \label{tab:table}}
\tablehead{\\
\hline\
\textit{Star} & \textit{Value} & \textit{Prior} &  & \\
\hline
$R_\star [R_\odot]$ & & $\mathcal{G}(1.305, 0.07)$ & & \\
$u_1$ & & $\mathcal{U}[0, 1]$ in $q_1$ & & \\
$u_2$ & & $\mathcal{U}[0, 1]$ in $q_2$ & & \\
$P_{rot}$ [days] & & $\mathcal{G}($ln$ 2.87, 2)$ & & \\
ln($A$ [ppt]) & & & & \\
ln($Q_0$) & & $\mathcal{H}(\sigma=2)$ & & \\
$\Delta Q_0$ & & $\mathcal{G}(0, 2)$ & & \\
$\rho_\textrm{SHO}$ & & $\mathcal{G}(0, 10)$ & & \\
$\sigma_\textrm{SHO}$ & & $\mathcal{G}(\sigma_\textrm{flux}, 10)$ & & \\
f [ppt] & & & & \\
mix & & & & \\
\hline\
\textit{Light Curve} & \textit{Value} & \textit{Prior} &  & \\
\hline
trend term a & & $\mathcal{G}(0, 0.01)$ & & \\
trend term b & & $\mathcal{G}(0, 0.1)$ & & \\
trend term c & & $\mathcal{G}(0, 1)$ & & \\
$\sigma_l$ & & $\mathcal{G}($ln$(0.1\sigma_\textrm{flux}), 10)$  & & \\
$\sigma_j$ & & $\mathcal{G}($ln$(0.1\sigma_\textrm{flux}), 10)$  & & \\
\hline\
\textit{Planets} & \textit{c} & \textit{d} & \textit{b} & \textit{e}\\
\hline
P [days]               &  &  &  &  \\
$T_0$ [BJD - 2457000]  &  &  &  &  \\
Depth [ppt]            &  &  &  &  \\
$R_p/R_\star$          &  &  &  &  \\
$a/R_\star$            &  &  &  &  \\
$b$                    &  &  &  &  \\
$e$ [$^\circ$]         &  &  &  &  \\
\hline\
\textit{Priors} & \textit{c} & \textit{d} & \textit{b} & \textit{e}\\
\hline
log($P$ [days]) & $\mathcal{G}($ln$ 8.25, 1)$ & $\mathcal{G}($ln$ 12.40, 1)$& $\mathcal{G}($ln$ 24.14, 1)$ & $\mathcal{G}($ln$ 36.70, 1)$\\
$T_0$ [BJD - 2457000] & $\mathcal{G}(4648.53,0.1)$ & $\mathcal{G}(4645.4,0.1)$ & $\mathcal{G}(4648.1,0.1)$ & $\mathcal{G}(4648.8,0.1)$ \\
log(depth [ppt]) & $\mathcal{G}($ln$ 1.45, 1)$ & $\mathcal{G}($ln$ 1.90, 1)$ & $\mathcal{G}($ln$ 4.90, 1)$ & $\mathcal{G}($ln$ 3.73, 1)$ \\
$b$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ & $\mathcal{U}[0, 1]$ \\
duration [days] & $\mathcal{G}($ln$ 0.19, 1)$ & $\mathcal{G}($ln$ 0.23, 1)$ & $\mathcal{G}($ln$ 0.27, 1)$ &  $\mathcal{G}($ln$ 0.31, 1)$
}
\startdata
\enddata
\tablecomments{Priors are noted for parameters that were directly sampled. The distributions are as follows -- $\mathcal{G}$: Gaussian; $\mathcal{H}$: Half-normal; $\mathcal{U}$: Uniform. $\sigma_\textrm{flux}$ is the standard deviation of the light curve}
\end{deluxetable*}
